Reference label transfer from the fetal full reference (Cao et al.) for `r params$sample_id`

### 2024-08-28 analyses/cell-type-wilms-tumor-06/notebook_template/02a_label-transfer_fetal_full_reference_Cao.Rmd
Update 02a_label-transfer_fetal_full_reference_Cao.Rmd

```{r packages, message=FALSE, warning=FALSE}
library(SingleCellExperiment)

library("Seurat")
library(sctransform)
library(Azimuth)
library(SeuratData)

library(assertthat)
library(viridis)
library(SCpubr)
library(tidyverse)
library(patchwork)

>>>>

```{r packages, message=FALSE, warning=FALSE}
library("Seurat")
library(SeuratData)
library(sctransform)
library(Azimuth)
library(SCpubr)
library(tidyverse)
library(patchwork)
library(SingleCellExperiment)
